---
title: "Exploring the World with Leaflet"
author: "Raghav Kapoor"
date: "30 Oct 2025"
output:
  html_document:
    theme: flatly
    highlight: tango
---


```{r setup, include=FALSE}
# ---- SETUP ----
if (!requireNamespace("leaflet", quietly = TRUE)) {
  install.packages("leaflet")
}
library(leaflet)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

<style>
@import url('https://fonts.googleapis.com/css2?family=Poppins:wght@300;400;500;600&display=swap');

/* ---- Clean Poppins Styling ---- */
body {
  font-family: 'Poppins', sans-serif;
  background: linear-gradient(to bottom right, #fffef8, #eefaf6);
  color: #1e272e;
  line-height: 1.7;
  padding: 25px;
}

h1, h2, h3 {
  font-family: 'Poppins', sans-serif;
  font-weight: 600;
  color: #00796b;
  text-align: center;
}

h1 {
  font-size: 2.3em;
  letter-spacing: 0.5px;
  margin-top: 25px;
  text-shadow: 1px 1px #dff9fb;
}

h2 {
  margin-top: 40px;
  color: #00897b;
  border-bottom: 3px solid #fbc02d;
  padding-bottom: 6px;
}

p {
  font-size: 1.05em;
  text-align: justify;
  margin: 12px 0;
}

.leaflet-container {
  border-radius: 12px !important;
  box-shadow: 0 4px 10px rgba(0,0,0,0.2);
  margin-top: 25px;
}

hr {
  border-top: 2px dashed #fbc02d;
  margin: 40px 0;
}

footer {
  text-align: center;
  margin-top: 40px;
  font-size: 0.95em;
  color: #00796b;
  font-weight: 500;
}
</style>

# Interactive Leaflet Map

This webpage demonstrates how to use the **Leaflet** package in **R Markdown** to create an interactive world map.  
It includes two map layers — **Default** and **Satellite** — so users can switch between them while exploring.  
You can zoom, drag, and click the markers to learn more about major world cities.

```{r leaflet-map, echo=FALSE}
# ---- INTERACTIVE MAP (Default + Satellite) ----
leaflet() %>%
  addTiles(group = "Default") %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") %>%

  # North America
  addMarkers(lng = -74.0060, lat = 40.7128, popup = "<b>New York City, USA</b><br>The city that never sleeps.", group = "Cities") %>%
  addMarkers(lng = -118.2437, lat = 34.0522, popup = "<b>Los Angeles, USA</b><br>City of Angels with sunny skies.", group = "Cities") %>%
  addMarkers(lng = -123.1207, lat = 49.2827, popup = "<b>Vancouver, Canada</b><br>Where mountains meet the ocean.", group = "Cities") %>%
  addMarkers(lng = -99.1332, lat = 19.4326, popup = "<b>Mexico City, Mexico</b><br>Vibrant capital rich with history.", group = "Cities") %>%

  # South America
  addMarkers(lng = -43.1729, lat = -22.9068, popup = "<b>Rio de Janeiro, Brazil</b><br>Famous for Carnival and beaches.", group = "Cities") %>%
  addMarkers(lng = -58.3816, lat = -34.6037, popup = "<b>Buenos Aires, Argentina</b><br>Known for tango and architecture.", group = "Cities") %>%

  # Europe
  addMarkers(lng = -0.1276, lat = 51.5072, popup = "<b>London, UK</b><br>Historic capital of culture and tradition.", group = "Cities") %>%
  addMarkers(lng = 2.3522, lat = 48.8566, popup = "<b>Paris, France</b><br>City of Lights and art.", group = "Cities") %>%
  addMarkers(lng = 12.4964, lat = 41.9028, popup = "<b>Rome, Italy</b><br>Home to ancient landmarks and vibrant food culture.", group = "Cities") %>%

  # Africa
  addMarkers(lng = 31.1342, lat = 29.9792, popup = "<b>Giza, Egypt</b><br>Home of the Great Pyramids.", group = "Cities") %>%
  addMarkers(lng = 18.4241, lat = -33.9249, popup = "<b>Cape Town, South Africa</b><br>Located at the foot of Table Mountain.", group = "Cities") %>%

  # Asia
  addMarkers(lng = 139.6917, lat = 35.6895, popup = "<b>Tokyo, Japan</b><br>Where tradition meets modern technology.", group = "Cities") %>%
  addMarkers(lng = 77.2090, lat = 28.6139, popup = "<b>New Delhi, India</b><br>Capital city rich in history and color.", group = "Cities") %>%
  addMarkers(lng = 103.8198, lat = 1.3521, popup = "<b>Singapore</b><br>Small island city-state with global influence.", group = "Cities") %>%

  # Oceania
  addMarkers(lng = 151.2093, lat = -33.8688, popup = "<b>Sydney, Australia</b><br>Known for the Opera House and beaches.", group = "Cities") %>%

  # Controls
  addLayersControl(
    baseGroups = c("Default", "Satellite"),
    overlayGroups = c("Cities"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addScaleBar(position = "bottomleft")
```

# About This Page

This project shows how to embed an **interactive map** into an R Markdown webpage using the **Leaflet** package.  
It demonstrates adding basic map layers, custom markers, and descriptive popups for multiple cities.

### Page Details
- **Created on:** `r Sys.Date()`  
- **Author:** Saanie Naqvi  
- **Purpose:** To apply R Markdown and Leaflet for geographic visualization.  
- **Tools Used:** R • R Markdown • Leaflet • HTML Widgets  

# Reflection

This project helped me understand how geographic data can be visualized interactively in R.  
The Leaflet package made it simple to combine maps, markers, and descriptive text into one web-based display.  
Keeping the design minimal with only essential map layers ensured that the page loads quickly while still being visually engaging.

<hr>

<footer>
Created with R Markdown and Leaflet.  
<br>Interactive world map featuring major cities.
</footer>
